HTW Model e2

### 2024-02-24 Model/htw_model_e2.qmd
reorganize sections

file_name <- "e2_n_iter_50_ntry_200_2506"
#file_name <- "n_iter_400_ntry_100_2944"

@@

#### Subjects with biggest differential favoring ALM
```{r}
#| fig-height: 6
#| fig-width: 12
vAlm <- c(307,331,197); cAlm <- c(372,298,299)

>>>>

file_name <- "e2_n_iter_50_ntry_200_2506"
#file_name <- "n_iter_400_ntry_100_2944"
file_name <- "e2_n_iter_100_ntry_200_3436"

@@

#### Subjects with biggest differential favoring ALM
```{r}
#| fig-height: 6
#| fig-width: 12
vAlm <- c(307,331,197); cAlm <- c(372,173,157)
